Altering Backward Pass Gradients improves Convergence

### 2022-09-15 paper.tex
Modifications 1
Modifications 2

@@

\newpage \subsection{ResNet-18 Per Layer Index Diagram}

For the layer indices used in figures \ref{fig:norm_plots}, \ref{fig:high_bs},
\ref{fig:agc_pgt}, we provide a block diagram depicting the different convolutional
layers of ResNet-18 with corresponding layer indices in Fig. \ref{fig:resnet18}. Each
layer represents a convolutional layer, with the layer index and the number of filters
denoted alongside it. Downsampling convolutional layers in skip connections are drawn
and their layer indices are shown on the skip connection paths.

>>>>

Self-knowledge distillation is used in many papers in different ways, which mainly
focuses on improving the performance of the model by either creating multiple ensemble
student models \cite{zhang2018deep}, using different distorted versions of same data
with two different versions of a single network which guides one another
\cite{xu2019data} or injecting multiple sub-modules in the network to improve its
capacity \cite{zhang2019your}. However none of these methods use normal traditional
training without introducing sub-modules in the architecture. PGT differs from
self-knowledge distillation as it neither introduces any additional sub-modules nor
creates different ensembles to improve the performance of the model. PGT follows the
standard neural network training mechanism with a single change which is altering the
last layer's gradients in the backward pass.

@@

\newpage \subsection{ResNet-18 Layer Index Diagram}

For the layer indices used in figures Fig. \ref{fig:norm_plots}, \ref{fig:high_bs},
\ref{fig:agc_pgt}, we provide a block diagram depicting the different convolutional
layers of ResNet-18 with corresponding layer indices in Fig. \ref{fig:resnet18}. Each
layer represents a convolutional layer, with the layer index and the number of filters
denoted alongside it. Downsampling convolutional layers in skip connections are drawn
and their layer indices are shown on the skip connection paths.
